Comparing probabilistic predictive models applied to football

### 2015-07-07 template.tex
Resolvendo conflito.

	How can we fairly rank the various predictive models?
	A way of doing this is by using proper scoring rules, where
	the score may be interpreted as a numerical measure of how inaccurate was a given probabilistic prediction.

>>>>

	One way of fairly rank the various predictive models is by using proper scoring rules, where
	the score may be interpreted as a numerical measure of how inaccurate was a given probabilistic prediction.
